Search techniques for gaussian mixture modelling with Minimum Message Length, with applications to the origin of our Galaxy

### 2018-09-10 article/ms.tex
correct bounds on slogw

\begin{enumerate}
    \item The weights are distributed uniformly such that $w_k = 1/K$ and
          \begin{equation}
                \sum_{k=1}^{K}\log\weight_k = \sum_{k=1}^{K}\log{\frac{1}{K}} =-K\log{K} \quad .
          \end{equation}
    \item The weights are distributed such that $K - 1$ components each 
          describe just one data point $w_{1..K-1} = 1/N$, and the remaining 
          component describes all other data points $w_{K} = 1 - (K-1)/N$
          as $\sum_{k=1}^{K}\weight_k = 1$. At this extreme,
          \begin{equation}
                \sum_{k=1}^{K}\log\weight_k = (K-1)\log\frac{1}{N} + \log\left(1 - \frac{K - 1}{N}\right)
          \end{equation}
          \noindent{}and by making use of the identity 
            $\log{(a-b)} = \log{a} + \log{(1 - \frac{b}{a})}$
          we can simplify this expression to:
          \begin{equation}
                \sum_{k=1}^{K}\log\weight_k = \log{(N-K+1)} - K\log{N} \quad .
          \end{equation}
\end{enumerate}

\noindent{}Thus, for any finite mixture of $K$ Gaussian components we have 
derived the bounds
\begin{equation}
-K\log{K} \quad \leq \quad \sum_{k=1}^{K}\log\weight_k \quad \leq \quad - K\log{K} + \log(N + 1 - K)
\end{equation}
\noindent{}which gives us analytic expressions for the upper and lower value 
of $I_1$, regardless of the values of $\vec{\weight}$, for any mixture, and
bounds on $I_{1}$ can be derived from just $\{K, N, D\}$.

>>>>

\begin{enumerate}
    \item The weights are distributed uniformly such that $w_k = 1/K$ and
          \begin{equation}
                \sum_{k=1}^{K}\log\weight_k = \sum_{k=1}^{K}\log{\frac{1}{K}} =-K\log{K} \quad .
          \end{equation}
    \item The weights are distributed such that $K - 1$ components each 
          describe just two data points $w_{1..K-1} = 2/N$, and the remaining 
          component describes all other data points $w_{K} = 1 - (K-1)\frac{2}{N}$
          as $\sum_{k=1}^{K}\weight_k = 1$. At this extreme,
          %\begin{equation}
          %      \sum_{k=1}^{K}\log\weight_k = (K-1)\log\frac{1}{N} + \log\left(1 - \frac{K - 1}{N}\right)
          %\end{equation}
          \begin{equation}
            \sum_{k=1}^{K}\log\weight_k = (K - 1)\log\frac{2}{N} + \log\left(1 - \frac{2(K - 1)}{N}\right)
          \end{equation}

          \noindent{}and by making use of the identity 
            $\log{(a-b)} = \log{a} + \log{(1 - \frac{b}{a})}$
          we can simplify this expression to:
          \begin{equation}
            \sum_{k=1}^{K}\log\weight_k = (K - 1)\log{2} - K\log{N} + \log{(N - 2K + 2)}
          \end{equation}
          %\begin{equation}
          %      \sum_{k=1}^{K}\log\weight_k = \log{(N-K+1)} - K\log{N} \quad .
          %\end{equation}
\end{enumerate}

\noindent{}Thus, for any finite mixture of $K$ Gaussian components we have 
derived the bounds
\begin{equation}
-K\log{K} \quad \leq \quad \sum_{k=1}^{K}\log\weight_k \quad \leq \quad (K - 1)\log{2} - K\log{N} + \log{(N - 2K + 2)}
\end{equation}
\noindent{}which gives us analytic expressions for the upper and lower value 
of $I_1$, regardless of the values of $\vec{\weight}$, for any mixture, and
bounds on $I_{1}$ can be derived from just $\{K, N, D\}$.
